Pre-processing high frequency animal tracking data

### 2020-09-18 03_smoothing_tracks.Rmd

# Smoothing positioning errors

@@

## Introducing 'reasonable' psoitioning errors {-}

@@

```{r read_sim_data_2}
# read in the data
data <- fread("data/data_sim.csv")

# add small position errors to either X or Y
data_with_errors <- copy(data)
data_with_errors[, `:=`(x = x + rnorm(nrow(data), mean = 0, sd = 0.005),
                        y = y + rnorm(nrow(data), mean = 0, sd = 0.005))]

# plot for sanity
ggplot()+
  geom_point(data = data_with_errors,
             aes(x, y),
             shape = 16,
             size = 0.2)+
  theme_void()
```

@@

```{r}
# make a copy
data_median_smooth <- copy(data_with_errors)
data_median_smooth <- atl_median_smooth(data_median_smooth,
                                        x = "x", 
                                        y = "y",
                                        time = "time",
                                        moving_window = 5)

# plot for sanity
ggplot()+
  geom_path(data = data,
            aes(x, y),
            colour = "blue",
            size = 2)+
  geom_point(data = data_with_errors,
             aes(x, y),
             shape = 16,
             size = 0.2)+
  geom_path(data = data_median_smooth,
            aes(x, y),
            colour = "red",
            size = 1)+
  theme_void()
```

>>>>

# Smoothing tracks and aggregating dat

@@

## Reading in data {-}

@@

```{r read_sim_data_2}
# read in the data
data <- fread("data/data_sim.csv")[5000:10000, ]
# data with small scale errors but no reflections or outliers
data_errors <- fread("data/data_no_reflection.csv")
```

@@

```{r}
# smooth the data
list_of_smooths <- lapply(c(3, 5, 11, 21), function(z) {
  data_copy <- copy(data_errors)
  atl_median_smooth(data = data_copy,
                    x = "x", 
                    y = "y",
                    time = "time",
                    moving_window = z)
})
```

```{r}
# prepare data to plot
# make list of data to plot
data_plot <- append(list(data, data_errors), list_of_smooths)

# make plot list
plots <- lapply(data_plot, function(df) {
  ggplot(data = df)+

    geom_point(aes(x, y),
              col = "grey", 
              alpha = 0.1,
              shape = 16)+
    geom_path(aes(x, y),
              col = "red", 
              alpha = 0.5)+
    coord_equal(xlim = c(0.5, 1),
                ylim = c(0.5, 1)) +
    theme_test()+
    theme(axis.text = element_blank(),
          axis.title = element_blank())
})

# wrap plots
plot_figure <- wrap_plots(plots) +
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

plot_figure

# save figure
ggsave(plot_figure, filename = "figures/fig_median_smooth.png",
       width = 185, height = 185 * 2 / 3, units = "mm")
```

## Aggregating data

```{r}
# choose the data
data_agg <- copy(data)

list_of_agg <- lapply(c(10, 30, 120), function(z) {
  atl_thin_data(data = data_agg,
                interval = z,
                method = "aggregate")
})
```

```{r}
# plot
data_plot <- append(list(data[, SD := 0]), list_of_agg)

# make plot list
plots <- lapply(data_plot, function(df) {
  ggplot(data = df)+

    geom_point(aes(x, y, size = SD), 
              alpha = 0.5,
              shape = 16, show.legend = F)+
    geom_path(aes(x, y),
              col = "red", 
              alpha = 1, lwd = 0.2)+
    coord_equal()+
    theme_test()+
    theme(axis.text = element_blank(),
          axis.title = element_blank())
})

# wrap plots
plot_figure <- wrap_plots(plots, ncol = 4) +
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

plot_figure

# save figure
ggsave(plot_figure, filename = "figures/fig_aggregate_data.png",
       width = 185, height = 90, units = "mm")
```

### 2020-09-18 11_residence_patch.Rmd

>>>>

```{r}
# read in the data
data <- fread("data/data_sim.csv")[5000:10000, ]
data[, id := "a"]

# make residence patch
patch <- atl_res_patch(data, buffer_radius = 0.01, 
                       lim_spat_indep = 0.05, lim_time_indep = 5)

patch_sf <- atl_patch_summary(patch_data = patch, which_data = "summary", buffer_radius = 0.01)
```
